
% sciences/science/intro.tex

\setcounter{section}{-1}
\section{Introduction}\label{sec:intro}

Solutions are proposed in Sections \ref{sec:mechanics}-\ref{sec:quantum} for exercises selected from \cite{TM, QM}.
Common notation is reviewed in Section \ref{sec:notation}.

\subsection{Notation}\label{sec:notation}

Denote the totally ordered field of real numbers by
\begin{align*}
	\left\langle \R, \R \times \R \xrightarrow{+} \R, 0, \R \times \R \xrightarrow{\cdot} \R, 1, \leq \right\rangle
\end{align*}
and the field of complex numbers as follows.
\begin{align*}
	\left\langle \C, \C \times \C \xrightarrow{+} \C, 0, \C \times \C \xrightarrow{\cdot} \C, 1 \right\rangle
\end{align*}
The field $\C$ of complex numbers carries the field involution $\C \xrightarrow{\overline{\bullet}} \C$ of complex conjugation.
Let $\C \times \C \xrightarrow{\braket{\bullet \mid \star}} \C$ denote the standard complex inner product on $\C$ given by $\braket{z \mid w} = \overline{z} w$, which is linear in $w$ and conjugate-linear in $z$.
The subset $\R_{\geq 0} = [0, \infty)$ of non-negative real numbers forms a totally ordered commutative semiring with multiplicative identity $1$.
Denote the totally ordered semiring of natural numbers as follows.
\begin{align*}
	\left\langle \N, \N \times \N \xrightarrow{+} \N, 0, \N \times \N \xrightarrow{\cdot} \N, 1, \leq \right\rangle
\end{align*}
For any natural $n \in \N$, denote the standard $n$-dimensional complex Hilbert space by
\begin{align*}
	\left\langle \C^n, \C^n \times \C^n \xrightarrow{+} \C^n, \vzero, \C \times \C^n \xrightarrow{\cdot} \C^n, \C^n \times \C^n \xrightarrow{\braket{\bullet \mid \star}} \C, \C^n \xrightarrow{\|\bullet\|} \R_{\geq 0} \right\rangle
\end{align*}
and the $n$-dimensional real Euclidean space as follows.
\begin{align*}
	\left\langle \R^n, \R^n \times \R^n \xrightarrow{+} \R^n, \vzero, \R \times \R^n \xrightarrow{\cdot} \R^n, \R^n \times \R^n \xrightarrow{\cdot} \R, \R^n \xrightarrow{\|\bullet\|} \R_{\geq 0} \right\rangle
\end{align*}
Let $\Z_+$ be the totally ordered semigroup of positive integers.

\subsubsection{Euclidean plane}
The Euclidean plane is the $2$-dimensional real Euclidean vector space $\R^2$ equipped with the standard Euclidean dot product.
The (ordered, orthonormal) Cartesian basis $e = \left(\vx, \vy\right)$ consists of the unit vectors given below.
\begin{align*}
	\vx & =
	\begin{bmatrix}
		1 \\ 0
	\end{bmatrix}
	    &
	\vy & =
	\begin{bmatrix}
		0 \\ 1
	\end{bmatrix}
\end{align*}
The Cartesian plane is the Euclidean plane equipped with the Cartesian basis.
The Cartesian components of a vector $\vr \in \R^2$ are the quantities below.
\begin{align*}
	x & = \vx \cdot \vr
	  &
	y & = \vy \cdot \vr
\end{align*}
Any such vector is given by $\vr = x \vx + y \vy$ and represented in the Cartesian basis by $\vr = \begin{bmatrix} x \\ y \end{bmatrix}$.
The norm of $\vr$ is denoted $r = \left\|\vr\right\|$ and is called the radial coordinate of $\vr$.
If $\vr \neq \vzero$, a polar angle of $\vr$ is a real number $\theta \in \R$ satisfying the equations below.
\begin{align*}
	x & = r \cos \theta
	  &
	y & = r \sin \theta
\end{align*}
Any two polar angles of $\vr$ differ by an integer multiple of $2 \pi$.
The vector $\vth$ perpendicular to $\vr = \begin{pmatrix} r \cos \theta \\ r \sin \theta \end{pmatrix}$ with $\left\|\vth\right\| = \left\|\vr\right\|$ is given by $\begin{pmatrix} - r \sin \theta \\ r \cos \theta \end{pmatrix}$.
Denote the unit vector in the direction of $\vr$ by $\hat{\vr} = \frac{1}{r} \vr$.

Associated with any $\vr \in \left(\R^2 \setminus \left\{\vzero\right\}\right)$ is the (ordered, orthonormal) polar basis $\left(\hat{\vr}, \hat{\vth}\right)$ consisting of the unit vectors $\hat{\vr} = \frac{1}{r} \vr$ and $\hat{\theta} = \frac{1}{r} \vth$ perpendicular to it; they can be expressed as follows.
\begin{align*}
	\hat{\vr}  & =
	\begin{bmatrix}
		\cos \theta \\
		\sin \theta
	\end{bmatrix}
	           &
	\hat{\vth} & =
	\begin{bmatrix}
		- \sin \theta \\
		\phantom{+} \cos \theta
	\end{bmatrix}
\end{align*}

Their derivatives with respect to the polar angle $\theta$ are given below.
\begin{align*}
	\frac{\partial \hat{\vr}}{\partial \theta}  & = \hat{\vth}
	                                            &
	\frac{\partial \hat{\vth}}{\partial \theta} & = - \hat{\vr}
\end{align*}
The position corresponding to polar coordinates $(r, \theta)$ is $\vr = r \hat{\vr}$.
Denote the punctured Euclidean plane by $\R^2 \setminus \vzero$.

While round brackets are often used for $\R^2$ and other vector spaces, square brackets are used to denote vectors in $\R^2$ and their matrices.

\subsubsection{Euclidean space}
Denote the standard basis unit vectors in $\R^3$ as follows.
\begin{align*}
	\vx     & =
	\begin{pmatrix}
		1 \\ 0 \\ 0
	\end{pmatrix}
	        &
	\vy     & =
	\begin{pmatrix}
		0 \\ 1 \\ 0
	\end{pmatrix}
	        &
	\mbf{z} & =
	\begin{pmatrix}
		0 \\ 0 \\ 1
	\end{pmatrix}
\end{align*}
They form an orthonormal basis $e = (\vx, \vy, \mbf{z})$ of $\R^3$.
For any vector $\vec{n} \in \R^3$, denote its inner products with the standard basis vectors as follows.
\begin{align*}
	n_x & = \vx \cdot \vec{n}
	    &
	n_y & = \vy \cdot \vec{n}
	    &
	n_z & = \mbf{z} \cdot \vec{n}
\end{align*}
Any triple of real numbers $\begin{pmatrix} n_x \\ n_y \\ n_z\end{pmatrix}$ uniquely determines a vector $\vec{n} \in \R^3$ with those coordinates.
Let $S^2 = \left\{\, \hat{n} \in \R^3 \mid \|\hat{n}\| = 1\right\}$ denote the $2$-dimensional unit sphere about the origin in $\R^3$.

\subsubsection{Outline}

In what follows, each section herein corresponds to a book whose exercises are attempted and each subsection corresponds to a lecture from the corresponding book.

