
% /science/math.tex

\section*{Interlude on the mathematical sciences}
\addcontentsline{toc}{section}{Interlude on the mathematical sciences}

A few classical results needed for Section \ref{sec:quantum} are reviewed.

\subsection*{Units}

Let $L$ denote a Lagrangian.

\begin{remark}[Units of derivative of function on phase space]\label{rem:derivative}
	For any function $F(q, p)$ of a generalized coordinate $q$ and canonical momentum $p = \frac{\partial L}{\partial \dot{q}}$, the partial derivative $\frac{\partial F(q,p)}{\partial q}$ with respect to the generalized coordinate has units $\left[\frac{\partial F(q,p)}{\partial q}\right] = \frac{\left[F\right]}{\left[q\right]}$ and the partial derivative $\frac{\partial F(q,p)}{\partial p}$ with respect to the canonical momentum has units $\left[\frac{\partial F(q,p)}{\partial p}\right] = \frac{\left[F\right]}{\left[p\right]}$.
\end{remark}

\begin{proposition}
	For any functions $F\left(\vq, p\right)$ and $G\left(\vq, p\right)$, the product of partial derivatives has the dimensions below.
	\begin{align*}
		\left[\frac{\partial F}{\partial q_i} \frac{\partial G}{\partial p_i}\right] & = \frac{\left[F\right] \left[G\right]}{\left[q_i\right] \left[p_i\right]}
	\end{align*}
\end{proposition}
\begin{proof}
	The result follows from Remark \cite{rem:derivative}.
\end{proof}

\subsection*{Algebra}

Given the axis spanned by any unit vector $\hat{n}$, the rotation $r_{\hat{n}}^\theta$ of $\R^3$ about the axis by $\theta$ can be expressed by Rodrigues's rotation formula below.
\begin{align}\label{eqn:Rodrigues}
	r_{\hat{n}}^\theta \vec{m} & = \vec{m} \cos \theta + \left(\hat{n} \times \vec{m} \right) \sin \theta + \hat{n} \left(\hat{n} \cdot \vec{m}\right)\left(1 - \cos \theta\right)
\end{align}

Let $\mA$ denote an operator on a finite-dimensional vector space.

Recall the \emph{exponential} of $\mA$ is the operator $\exp\p{\mA} = e^{\mA}$ defined by $\dsp \sum_{k=0}^\infty \frac{1}{k!} \mA^k$.

\subsubsection*{Linear algebra}

Recall \emph{involutivity} of $\mA$ is the condition that $\mA^2 = I$.
If $\mA$ is an involution, then it holds for any natural $k \in \N$ that $\mA^{2 k} = I$ and $\mA^{2 k + 1} = \mA$.

Let $\mA$ be an involution on a finite-dimensional Hilbert space.
If the involution $\mA$ is Hermitian, then it is also unitary.
For any complex $z \in \C$, the exponential $\dsp \exp\p{z \mA} = \sum_{k=0}^\infty \left(\frac{z^{2k}}{(2k)!} \mA^{2k} + \frac{z^{2k+1}}{(2k+1)!} \mA^{2k+1}\right)$ of $z \mA$ is given by $\exp\p{z \mA} = \left(\cosh z\right) I + \left(\sinh z\right) \mA$.
For any real $\theta \in \R$, the exponential $\dsp \exp\p{i\theta \mA} = \left(\cosh i \theta\right) I + \left(\sinh i \theta\right) \mA$ is given below.
\begin{align}
	\exp\p{i \theta \mA} = \left(\cos \theta\right) I + i \left(\sin \theta\right) \mA
\end{align}

